### 2023-03-07 intro.qmd
update

| Pump                   | POC export/injection depth range | DOC injection depth range | Sequestration time potential (years) |
|-----------------|-------------------|-----------------|---------------------|
| Gravitational          | export depth - sediment          | None                      | N/A (142)                            |
| Mixed layer            | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Eddy subduction        | 150 - 400 m                      | 150 - 400 m               | up to 150 (N/A)                      |
| Large-scale subduction | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Diel migration         | 200 - 600 m                      | None                      | up to 250 (150$^{c}$)                |
| Seasonal migration     | 600 - 1,400 m$^{a}$              | None                      | up to 500 (N/A)                      |

>>>>

| Pump                   | POC export/injection depth range | DOC injection depth range | Sequestration time potential (years) |
|------------------------|----------------------------------|---------------------------|--------------------------------------|
| Gravitational          | export depth - sediment          | None                      | N/A (142)                            |
| Mixed layer            | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Eddy subduction        | 150 - 400 m                      | 150 - 400 m               | up to 150 (N/A)                      |
| Large-scale subduction | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Diel migration         | 200 - 600 m                      | None                      | up to 250 (150$^{c}$)                |
| Seasonal migration     | 600 - 1,400 m$^{a}$              | None                      | up to 500 (N/A)                      |

### 2023-03-07 observingCarbonCycle.qmd
update

When we compare the $e-ratio$ maps (@fig-export-ratios) or the carbon export estimations of only six biogeochemical models (see @sec-biogeochem-models), we already observe significant differences. On the one hand, we see an increase in model complexity from empirical models to data-assimilated inverse models thanks to the increase in the quantity and quality of observations as well as well as a deeper understanding of the BCP (@sec-a-new-paradigm-for-the-bcp). On the other hand, each degree of complexity inevitably accumulates more uncertainty due to the increasing number of processing and modeling steps (@fig-bgc-models).

>>>>

When we compare the $e-ratio$ maps (@fig-export-ratios) or the carbon export estimations of only six biogeochemical models (see @sec-biogeochem-models), we already observe significant differences. On the one hand, we see an increase in model complexity from empirical models to data-assimilated inverse models thanks to the increase in the quantity and quality of observations as well as a deeper understanding of the BCP (@sec-a-new-paradigm-for-the-bcp). On the other hand, each degree of complexity inevitably accumulates more uncertainty due to the increasing number of processing and modeling steps (@fig-bgc-models).
